\cvsection{Experience}

\begin{cvexperienceentry}{Bank Zero}{Back End Developer}{July 2025 -- Present}{Hybrid, Bryanston}
  \cvitem{Performance Engineering: Re-engineered mission-critical batch processing jobs, achieving a 95\% reduction in latency. Refactored long-running 7-hour jobs to complete in 20–30 minutes.}
  \cvitem{Frontend Modernization: Developed responsive solutions using Angular and Material, implementing a migration to Tailwind to improve development efficiency.}
  \cvitem{Architecture & Design: Collaborate with stakeholders to design and integrate new modules into the core banking framework, focusing on scalable and resilient data flows.}
  \cvitem{EFT Processing: Manage high-throughput EFT data ingestion and processing systems, ensuring idempotency and parallel execution for maximum reliability.}
  \cvitem{Governance: Drive technical excellence by standardizing the Java/Spring ecosystem through documentation and design best practices.}
  \cvitem{Financial Systems: Work on implementing financial posting logic for sponsored banking products.}
\end{cvexperienceentry}

\begin{cvexperienceentry}{nter}{Full Stack Developer}{October 2022 -- July 2025}{Remote}
  \cvitem{System Development: Implemented robust backend systems using Spring Framework, Hibernate, and Azure services including Key Vault and Azure SQL.}
  \cvitem{Frontend Modernization: Developed responsive solutions using Angular and Material, implementing a migration to Tailwind to improve development efficiency.}
  \cvitem{Custom Features: Designed and developed an integration with Unlayer Editor for dynamic email template customization.}
  \cvitem{Architecture: Collaborated on comprehensive database modeling and software architecture design for scalable web applications.}
\end{cvexperienceentry}

\begin{cvexperienceentry}{Investec}{Software Developer}{February 2019 -- October 2022}{Sandton}
  \cvitem{API Development: Developed APIs for records management solutions, successfully integrating with Documentum and SQL-based databases.}
  \cvitem{Data Migration: Led a complex database migration from SQL to Documentum, designing custom tools and ensuring high data integrity.}
  \cvitem{Legacy Modernization: Modernized legacy communication systems (Email, SMS, Fax), updating XSLT transformations to improve compatibility and client impact.}
\end{cvexperienceentry}
